### 2016-06-17 thesis/intro/intro.tex
tmp commit

@@

It is now commonly understood that cancers are caused by dysregulation of various mechanisms or pathways that allow tumour cells to prolilferate, survive and migrate.
Many of these dysregulated pathways frequently occur in cancer cells, and these characteristic traits, commonly known as the ``Hallmarks of Cancer'', were first described by \citet{Hanahan2000}.

@@

Although much reseach has been conducted on the ``Hallmarks of Cancer'', the molecular processes underlying these hallmarks have still not been fully explained \citep{Hanahan2011}.
This is due to the

@@

\section{Obesity associated genetic signatures}
\label{sec:obsgene}

Literature review, focussing on \citet{Creighton2012} and \citet{Fuentes-Mattei2014}.

@@

\\

@@

\\
       Galileo asserted that the earth revolves the sun.(The asserting took place in the past, but the\\
       earth is still revolving around the sun. Note also that no source citation is needed here since it is a\\
       widely known and well-accepted fact that Galileo made this assertion.)\\
\\
       Sexual dimorphism in body size is common among butterflies  (Singer1982).(Note how this\\
       statement differs from one in which you refer to the researcher's work in the sentence: "Singer\\
       (1982) stated that sexual dimorphism in body size is common among butterflies." Here you use past\\
       tense to indicate what Singer reported, but present tense to indicate a research result that is\\
       unlikely to change.)\\
\\
       We chose Vietnam for this study because it has a long coastline. (Use past tense to indicate what\\
       you did [chose Vietnam], but present tense to indicate you assume that the length of Vietnam's\\
       coastline is unlikely to change.)\\
\\
       We used cornmeal to feed the fingerlings because it provides high nutritional content at a\\
       relatively low cost. (Past tense reflects what you did [used cornmeal], but present tense indicates\\
       that neither the nutritional content nor the cost of corn meal is likely to change.)\\
\\

@@

\\
       Table 3 shows that the main cause of weight increase was nutritional value of the feed. (Table 3\\
       will always show this; it is now a fact that is unlikely to change, and will be true whenever anyone\\
       reads this sentence, so use present tense.)\\
\\

@@

\\
       Weight increased as the nutritional value of feed increased. These results suggest that feeds\\
       higher in nutritional value contribute to greater weight gain in livestock. (Use past tense to\\
       indicate what you found [weight increased], but use present tense to suggest what the result\\
       implies.)\\

>>>>

\subsection{Prevalence of obesity}
\label{sub:prevalence_of_obesity}

\subsection{Obesity and cancer risk}
\label{sub:obesity_and_cancer_risk}

@@

% TODO: edit the starting sentence so it's not a copy from the beginning
It is now commonly understood that cancers are caused by dysregulation of various mechanisms or pathways that allow tumour cells to prolilferate, survive and migrate.
Many of these dysregulated pathways frequently occur in cancer cells, and these characteristic traits, commonly known as the ``Hallmarks of Cancer'', were first described by \citet{Hanahan2000}.

@@

Although much reseach has been conducted on the ``Hallmarks of Cancer'', the molecular processes underlying these hallmarks have still not been fully explained \citep{Hanahan2011}.
This is due to the fact that cancer cells develop progressively under selective pressures, and are also affected by many environmental factors \citep{Gatza2011}, which makes it difficult to identify causal factors of cancer development.
Furthermore, these external factors affect how the cancer cells respond to the environment, and may also cause cancer progression and/or drug resistance.

\subsection{Tumour heterogeneity}
\label{sub:tumour_heterogeneity}

@@

\section{Genetic signatures}
\label{sec:genetic_signatures}

Due to advances in sequencing technology over the last few years, many researchers have started to focus on bioinformatics based analyses of cancer cells to better understand the biology of cancer.
Advantages of this strategy are that very specific gene expression and/or mutational signatures for certain cancer subtypes can be identified from the analyses, which the researchers and clinicians can study in much greater depth and details.

% TODO: have a leading sentence that introduces the gene signatures

\subsection{Obesity associated genetic signatures}
\label{subsec:obesity_associated_genetic_signatures}

\subsubsection{ \textbf{\citet{Creighton2012} study}}
\label{ssub:creighton_study}

\subsubsection{ \textbf{\citet{Fuentes-Mattei2014} study}}
\label{ssub:fuentes_mattei_study}

\subsection{Pathway associated genetic signatures}
\label{sub:pathway_associated_genetic_signatures}

Talk about \citet{Gatza2010a}

@@

@@

       Galileo asserted that the earth revolves the sun.(The asserting took place in the past, but the\\
       earth is still revolving around the sun. Note also that no source citation is needed here since it is a\\
       widely known and well-accepted fact that Galileo made this assertion.)\\

       Sexual dimorphism in body size is common among butterflies  (Singer1982).(Note how this\\
       statement differs from one in which you refer to the researcher's work in the sentence: "Singer\\
       (1982) stated that sexual dimorphism in body size is common among butterflies." Here you use past\\
       tense to indicate what Singer reported, but present tense to indicate a research result that is\\
       unlikely to change.)\\

       We chose Vietnam for this study because it has a long coastline. (Use past tense to indicate what\\
       you did [chose Vietnam], but present tense to indicate you assume that the length of Vietnam's\\
       coastline is unlikely to change.)\\

       We used cornmeal to feed the fingerlings because it provides high nutritional content at a\\
       relatively low cost. (Past tense reflects what you did [used cornmeal], but present tense indicates\\
       that neither the nutritional content nor the cost of corn meal is likely to change.)\\

@@

       Table 3 shows that the main cause of weight increase was nutritional value of the feed. (Table 3\\
       will always show this; it is now a fact that is unlikely to change, and will be true whenever anyone\\
       reads this sentence, so use present tense.)\\

@@

       Weight increased as the nutritional value of feed increased. These results suggest that feeds\\
       higher in nutritional value contribute to greater weight gain in livestock. (Use past tense to\\
       indicate what you found [weight increased], but use present tense to suggest what the result\\
       implies.)\\
